### 2016-11-08 paper3.tex
Fixed labels

\subsection{Superbubble Feedback}
\begin{table*}
\input{figures3/z0_table.tex}
    \caption[Summary of MUGS2 galaxy properties]{Redshift 0 properties of the
    full MUGS2 sample.  All masses and particle counts are measured within a
    $R_{\rm vir}$ sphere centred on the halo, except for $M_{\rm central}$,
    which is measured within a $0.1\;R_{\rm vir}$ sphere.}
\label{z0_table}
\end{table*}
\begin{figure*}
    \includegraphics[width=\textwidth]{figures3/stellar_edge.eps}
    \includegraphics[width=\textwidth]{figures3/stellar_face.eps}
    \caption[Mock stellar images of MUGS2 galaxies]{Mock optical stellar
    observations of each MUGS2 galaxy.  RGB channels are calculated using
    \citet{Marigo2008} stellar populations.  The top three rows show the
    galaxies edge on, while the bottom three show the galaxies face on.  The
    galaxies are sorted in order of halo mass, and galaxies that overproduce
    stars are labelled with red.  These images do not include the effects of
    dust extinction}
    \label{stellar_image}
\end{figure*}

@@

The EAGLE simulations \citep{Crain2015} use a purely thermal
injection for SNII feedback.  The energy per SN depends on both the local
density and metallicity of the gas that feedback is deposited in, determined
using equation~\ref{eagle}.
\begin{equation}
    E_{\rm SN} = 0.3 +
    \frac{2.7}{1+\left(\frac{Z}{0.1\Zsun}\right)^{0.87}\left(\frac{n_H}{0.67\rm{cm}^{-3}}\right)^{-0.87}}
    \label{eagle}
\end{equation}
This gives a total SNII energy of $3\times10^{50}\;\rm{erg}$ in the limit of
infinite metallicity or zero density, and $3\times10^{51}\;\rm{erg}$ in the
limit of zero metallicity or infinite density.  The injection rate is thus
$5.2\times10^{48}\;\rm{erg}\Msun^{-1}$ to
$5.2\times10^{49}\;\rm{erg}\Msun^{-1}$, depending on the local gas properties.
Both the EAGLE and Illustris simulations also include feedback from AGN.

@@

\subsection{Redshift zero properties}
\begin{figure}
    \includegraphics[width=\textwidth]{figures3/column_edge.eps}
    \includegraphics[width=\textwidth]{figures3/column_face.eps}
    \caption[HI column density images for MUGS2 galaxies]{{\sc Hi} column
    density in each of the MUGS2 galaxies.  As in Fig.~\ref{stellar_image}, the
    top three rows show the galaxy edge on.}
    \label{gas_column}
\end{figure}
\begin{figure}
    \includegraphics[width=0.7\textwidth]{figures3/SMHMR.eps}
    \caption[MUGS2 stellar mass to halo mass relation]{Stellar mass versus halo
    mass at $z=0$.  The observed stellar mass to halo mass relation is from
    \citet{Hudson2015}'s weak lensing study of galaxies to $z=0.8$.  Galaxies
    that fall within this range are shown as blue squares, while galaxies above
    the curve (those which form too many stars) are shown as red circles.  For
    comparison, the black stars show galaxies from the NIHAO sample
    \citep{Wang2015}.}
    \label{SMHMR}
\end{figure}
\begin{figure}
    \includegraphics[width=0.7\textwidth]{figures3/rotcurve.eps}
    \caption[MUGS2 rotation curves]{As is clear from the above rotation curves,
    galaxies which overproduce stars (shown in dotted red) also have large
    central concentrations, giving steeply peaked rotation curves inconsistent
    with those seen in local $L*$ galaxies.  Galaxies with well-regulated star
    formation have flat rotation curves (shown in solid blue).}
    \label{rotation_curve}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{figures3/stellar_central.eps}
    \caption[Stellar mass vs. central baryonic mass in MUGS2 galaxies]{The stellar mass and the central baryonic mass show a tight
        correlation.  For the well-regulated population, roughly $40\%$ of the
        central baryons are stars, while for the unregulated population has
        converted $\sim70\%$ of the central baryon mass into stars.}
    \label{stellar_central}
\end{figure}
\begin{figure}
    \includegraphics[width=0.63\textwidth]{figures3/phase.eps}
    \caption[Gas phase diagram in two MUGS2 galaxies]{Gas phase diagrams for a
    well-regulated galaxy (g24334) and an unregulated galaxy (g19195).  Colour
    shows the amount of mass at a given $\rho-T$ point.  The top phase diagram
    shows the characteristic slope for adiabatic (dashed line) and isobaric
    (dotted line) processes.  As can be seen, both galaxies are qualitatively
    the same.  Both show the equilibrium cooling curve below $10^4\K$, and both
    show the adiabatic evolution of superbubble-heated gas as it leaves the
    disc.}
    \label{phase}
\end{figure}

The general properties of each galaxy at $z=0$ can be found in
Table~\ref{z0_table}.  $\lambda'$ is the dimensionless spin parameter of the
halo, defined by \citet{Bullock2001} as $\lambda'=J/\sqrt{2GM_{\rm vir}^3R_{\rm vir}}$.
$f_b$ is the baryon fraction of the halo.  $z_{1/2}$ and $z_{\rm lmm}$ are the
redshifts at which the halo reaches half of its final mass, and the redshift of
last major merger respectively.  Major mergers are defined to match
\citet{Stinson2010}, as a merger with a halo containing at least $1/3$ the
stellar mass of the main progenitor.  $M_{\rm vir}$, $M_*$, and $M_{\rm gas}$ are the
masses of the full halo, the stellar component, and the gas component
respectively within the virial radius.  $\rm{SFR_{\rm z=0}}$ is the redshift 0 
SFR, averaged over the previous $100\Myr$.  The virial radius
is defined as the radius around the halo such that the enclosed density is 200
times the critical density ($\rho=200\rho_{\rm crit}$).  While we used the same
definitions for quantities reported in \citet{Stinson2010}, every value reported
here is derived from the new MUGS2 simulations.  We also define a {\it central}
region of the halo, which contains the disc and the majority of the stars within
the halo.  The baryon mass within this region is given as $M_{\rm central}$  This
central region is simply a sphere of radius $0.1R_{\rm vir}$.

Mock stellar observations and {\sc Hi} column images of these galaxies can be
seen in Figs~\ref{stellar_image} and~\ref{gas_column}.  The labels on each of
these images are coloured red if they are in the `unregulated' population
discussed in the next section.  The varied merger history of these galaxies is
evident in these images: companions can be seen in three galaxies (g21647,
g22795, g4145), tidal tails are evident in another  (g19195), and strong bars
exist in another two (g28547, g24334).

The {\sc Hi} column density shown in Fig.~\ref{gas_column} shows, as was seen in
\citet{Keller2015}, large quantities of extraplanar {\sc Hi} gas, driven up by
outflows from the galaxy disc.  {\sc Hi} gas above the galactic plane has been seen
since \citet{Muller1963}.  \citet{Lockman1984} found similar column densities to
what is seen here to heights of $1.5\kpc$.  High-velocity clouds of relatively
dense ($\sim0.1\; \rm{cm^{-3}}$ gas have also been seen both leaving and
returning to the galaxy \citep{Wakker1997}.  Diffuse {\sc Hi} gas has been observed
out to $\sim300\kpc$ in absorption features of numerous nearby galaxies
\citep{Wakker2009,Prochaska2011}.  \citet{Werk2014} surveyed a number of
galaxies in the COS-haloes survey, and found that typical $L*$ galaxies contain
$\sim5 \times10^{10}\Msun$ of cool gas in their CGM.  The face-on {\sc Hi}
distribution for all but a handful of the unregulated (see the following
section) follow the \citet{Broeils1997} {\sc Hi} mass-size relation, with {\sc Hi} column
densities falling below $1\Msun\pc^{-2}$ at radii of $10-20\kpc$.  This is well
within the intrinsic scatter found in the recent observational study of
\citet{Wang2016}.

\subsection{Stellar Mass Runaway}
\begin{figure}
    \includegraphics[width=0.7\textwidth]{figures3/stellar_fraction_time.eps}
    \caption[Stellar mass fraction evolution in MUGS2]{Stellar mass fraction
    versus time.  As is clear, for the unregulated population the buildup of
    stellar mass above $\sim3\%$ of the halo mass happens very rapidly, often on
    time-scales of $\sim1\Gyr$.  The runaway in the unregulated population stops
    simply when the disc has been sufficiently depleted of gas that little
    remains to form new stars.}
    \label{stellar_fraction_time}
\end{figure}
As can be seen in Fig.~\ref{SMHMR}, roughly half of these galaxies fall within
the expected $z=0$ stellar mass to halo mass relation (SMHMR).  The grey band
shown in the figure is the $2\sigma$ confidence region in the observed SMHMR
from \citet{Hudson2015}, which used the CFHTLens weak lensing survey to produce
a fully-observational SMHMR, without the uncertainties of the using dark
matter-only simulations that are needed for abundance matching techniques (the
\citet{Hudson2015} SMHMR is consistent with past abundance matching estimates
such as \citet{Behroozi2013} and \citet{Moster2013}).  For the rest of this
paper, we will refer to the galaxies that fall within the $2\sigma$ confidence
interval for the observed SMHMR (i.e. galaxies where stellar feedback prevents
overproduction of stars) as {\it well-regulated}, and the galaxies where stellar
feedback fails to produce the correct SMHMR as {\it unregulated}.  No other
criterion is used for determining which population a galaxy falls into. In
addition to overproducing stars, these unregulated galaxies are qualitatively
redder and more bulge dominated, as can be seen in the mock stellar images of
Fig.~\ref{stellar_image}.  There appears to be no significant difference in
the redshift of the last major merger between the two populations, strongly
suggesting that the failure of stellar feedback to regulate the galaxies is not
simply a matter of recent or violent merging.  The rotation curves in
Fig.~\ref{rotation_curve} also show the distinct signature of massive bulges
formed by catastrophic angular momentum loss in the unregulated population.
\citet{vanDenBosch2001} showed that this can arise when gas simply traces the
dark matter distribution, without redistribution or ejection by feedback.  The
strong peaks (as high as $700\kms$ for g4720) come about from the central
concentration of baryons in the galaxy bulge.  Without exception, each of the
well-regulated galaxies shows a flat rotation curve, with no evidence of a
significant bulge component.  This matches the qualitative morphology seen in
Fig.~\ref{stellar_image}.

Fig.~\ref{stellar_central} shows that for the well-regulated population, the
stellar mass and central baryonic mass follow an extremely tight linear
relation, with a mean star formation efficiency (simply defined here as the
fraction of central baryons that are in stars) of $38\pm2\%$ over a Hubble time.
For the galaxies that fail to self-regulate, they exhibit a total star formation
efficiency of $70\pm10\%$, converting the majority of the baryons that collapse
on to their disc into stars.  Interestingly, the two populations can be divided
cleanly along the $M_{\rm central}=10^{11}\;\Msun$ or the
$M_*=5\times10^{10}\;\Msun$ axis.  This is clear evidence that what explains
the dichotomy here must involve the accretion (or the failure to remove!)
baryons from the central region of the halo, where the disc resides and stars
are formed.  These relations also help to explain some of the correlations seen
observationally, such as the critical mass of $3\times10^{10}\Msun$ that 
\citet{Kauffmann2003a} found dividing star forming and quenched galaxies in the
SDSS at low redshift.

The gas phase diagram of galaxies in the two populations is remarkably similar,
as can be seen in Fig.~\ref{phase}.  For a representative pair from each
population, of nearly equal halo mass, gas follows essentially the same
evolutionary path, characteristic of a superbubble-regulated ISM, as was shown in
\citet{Keller2015}.  Gas accretes from the halo,
building up a warm ISM at $T\sim10^4\K$.  Where that gas reaches densities of
$\sim 1\;$cm$^{-3}$, it begins to cool quickly and form stars.  Those stars begin to
explode as SN, and a hot superbubble is formed, with $T>10^7\K$.  As the bubble
grows, it's temperature falls as it both expands adiabatically and evaporates
the cold shell surrounding it.  This hot, buoyant gas leaves the disc, rising
through the CGM and cooling adiabatically as it goes.  What is remarkable here
is just how similar the phase diagrams of these two galaxies are.  The slight
differences are what we would expect from Table~\ref{z0_table}.  g19195 has
$\sim50\%$ less gas than g24334, and more than 3 times the SFR at $z=0$.  Thus,
there is less total material, especially in the warm and cold phases, and
slightly more of the very hot ($T>5\times10^7\K$) gas (the interiors of very young
superbubbles) as a consequence of the higher SFR.  What is important to take
away from these phase diagrams is that a well-regulated and unregulated galaxy
do not have any real difference in the phase behaviour of their gas.  There is
no runaway cooling, or failure of SN to generate hot gas:  what causes the
unregulated population to runaway is purely an effect of the outflow
effectiveness, which is set by the depth of the potential well.

\subsection{Time Evolution} 
\begin{figure}
    \includegraphics[width=0.7\textwidth]{figures3/SMHMR_time.eps}
    \caption[Stellar mass vs. halo mass evolution in MUGS2]{Stellar mass versus
    halo mass, as shown in Fig.~\ref{SMHMR}, but with trails added to show time
    evolution.  For halo masses below $\sim\rm{a\;few}\times10^{11}$, the
    evolution of the regulated and unregulated populations are
    indistinguishable.  The grey bar shows the $z=0$ SMHMR, as in
    Fig.~\ref{SMHMR}}
    \label{SMHMR_time}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{figures3/stellar_central_time.eps}
    \caption[Stellar mass vs. central baryonic mass evolution in MUGS2]{Stellar
    mass versus central baryon mass. The stellar mass here can be seen to vary
    much more smoothly over the evolution, without the slight `jump' seen in
    Fig.~\ref{stellar_fraction_time}.}
    \label{stellar_central_time}
\end{figure}

The obvious question that arises from the presence of these two (well-regulated
versus  unregulated) populations at $z=0$ is whether they are distinct through
their entire evolution, and if not, why/how do they diverge?  Previous work
suggests that a characteristic (halo or stellar) mass exists above which AGN
feedback is needed.  There is much uncertainty, however, about where this mass
exactly is, and how the transition from SN to AGN regulation actually works. We
should thus expect galaxies to begin diverging once this characteristic mass is
exceeded.  As Fig.~\ref{stellar_fraction_time} shows, the stellar mass
fraction for the two populations appear to follow similar evolutionary tracks
for some time (until past $z=0.5$ in the case of g19195, the galaxy which
diverges the latest).  However, once a galaxy begins to overproduce stars, it
appears to do so in a runaway, doubling or even tripling its stellar mass
fraction in less than a Gyr.

The similar early star formation history of the two populations is even more
clear if we look at the SMHMR's time evolution in Fig.~\ref{SMHMR_time}.  Here
we can see, that for galaxies with halo masses below a few $10^{11}\;\Msun$,
the stellar mass falls well within the expected SMHMR distribution, and the two
populations are indistinguishable.  The mass at which the populations begin to
diverge ( $M_*\sim10^{10}\;\Msun$ and $M_{\rm vir}\sim\operatorname{3-
5}\times10^{11}\;\Msun$) are quite close to the expected transition range
from \citet{Shankar2006} ( $M_*\sim1.2\times10^{10}\;\Msun$ and
$M_{\rm vir}\sim3\times10^{11}\;\Msun$).

The relatively smooth change in the $M_*-M_{\rm central}$ relation, shown in
Fig.~\ref{stellar_central_time}, shows that it is in fact the central baryon
mass that is more tightly correlated with the stellar mass than the total halo
mass (in galaxies regulated by SN feedback alone). In fact, it is likely that
some of the more massive galaxies in the well-regulated sample are on their way
to failing, but simply have not yet had enough time by $z=0$ to diverge
significantly from the observed SMHMR.  Once more than $\sim10^{11}\Msun$ of
baryons have accreted to the disc of a galaxy, SN alone appear to be unable to
halt the growth of stellar mass.  At this point, star formation efficiency of
the central disc begins to increase, from $\sim40$ to $\sim70$ per cent, resulting in
the differences seen in the two populations at $z=0$.  This accretion crisis, as
it continues to smaller scales, also explains the rotation profiles of the
unregulated population.  The overcollapse that results in runaway starformation
also builds a massive bulge, producing the peaked rotation curves seen in
Fig.~\ref{rotation_curve}.

\subsection{Galactic Outflows}
\begin{figure}
    \includegraphics[width=0.7\textwidth]{figures3/massloading_time.eps}
    \caption[Outflow mass loading evolution in MUGS2]{Outflow mass loading
    decreases as galaxies grow over time, as was previously shown by
    \citet{Keller2015}.  Here we see, when examining the mean mass loadings for
    the two populations (the well-regulated galaxies, where stellar feedback
    succeeds, and the unregulated galaxies, where it fails), that the
    unregulated galaxies have their mass loadings decrease sooner, and to lower
    values, than the well-regulated population.  The error bars here are the
    $1\sigma$ scatter in each population.}
    \label{massloading_time}
\end{figure}
\begin{figure}
    \includegraphics[width=0.7\textwidth]{figures3/massloading_halo.eps}
    \caption[Mass loading as a function of halo mass in MUGS2]{Unlike in the
    previous figure, if we look at mass loading as a function of halo mass, we
    instead see no significant difference between the two populations.  Instead,
    both follow a similar trajectory, and the haloes which fail to self-regulate
    do so simply because they reach a higher mass earlier.}
    \label{massloading_halo}
\end{figure}

@@

Fig.~\ref{SMHMR} shows that while the unregulated galaxies tend to be more
massive than the well-regulated ones, there is some overlap in the $M_{\rm
halo}=\operatorname{8-12}\times10^{12}\;\Msun$ range, where there are both
unregulated and well-regulated galaxies.  Figs~\ref{stellar_fraction_time}
and~\ref{SMHMR_time} show that the process of runaway star formation happens
rapidly, and can begins over a wide range of halo masses.  This is further
evidence that something beyond simply the mass of the halo that hosts a galaxy
is at play in determining whether or not SN fail to regulate the growth of that
galaxy.

>>>>

\subsection{Superbubble Feedback}
\begin{table*}
\input{figures3/z0_table.tex}
    \caption[Summary of MUGS2 galaxy properties]{Redshift 0 properties of the
    full MUGS2 sample.  All masses and particle counts are measured within a
    $R_{\rm vir}$ sphere centred on the halo, except for $M_{\rm central}$,
    which is measured within a $0.1\;R_{\rm vir}$ sphere.}
\label{z0_table3}
\end{table*}
\begin{figure*}
    \includegraphics[width=\textwidth]{figures3/stellar_edge.eps}
    \includegraphics[width=\textwidth]{figures3/stellar_face.eps}
    \caption[Mock stellar images of MUGS2 galaxies]{Mock optical stellar
    observations of each MUGS2 galaxy.  RGB channels are calculated using
    \citet{Marigo2008} stellar populations.  The top three rows show the
    galaxies edge on, while the bottom three show the galaxies face on.  The
    galaxies are sorted in order of halo mass, and galaxies that overproduce
    stars are labelled with red.  These images do not include the effects of
    dust extinction}
    \label{stellar_image3}
\end{figure*}

@@

The EAGLE simulations \citep{Crain2015} use a purely thermal
injection for SNII feedback.  The energy per SN depends on both the local
density and metallicity of the gas that feedback is deposited in, determined
using equation~\ref{eagle3}.
\begin{equation}
    E_{\rm SN} = 0.3 +
    \frac{2.7}{1+\left(\frac{Z}{0.1\Zsun}\right)^{0.87}\left(\frac{n_H}{0.67\rm{cm}^{-3}}\right)^{-0.87}}
    \label{eagle3}
\end{equation}
This gives a total SNII energy of $3\times10^{50}\;\rm{erg}$ in the limit of
infinite metallicity or zero density, and $3\times10^{51}\;\rm{erg}$ in the
limit of zero metallicity or infinite density.  The injection rate is thus
$5.2\times10^{48}\;\rm{erg}\Msun^{-1}$ to
$5.2\times10^{49}\;\rm{erg}\Msun^{-1}$, depending on the local gas properties.
Both the EAGLE and Illustris simulations also include feedback from AGN.

@@

\subsection{Redshift zero properties}
\begin{figure}
    \includegraphics[width=\textwidth]{figures3/column_edge.eps}
    \includegraphics[width=\textwidth]{figures3/column_face.eps}
    \caption[HI column density images for MUGS2 galaxies]{{\sc Hi} column
    density in each of the MUGS2 galaxies.  As in Fig.~\ref{stellar_image3}, the
    top three rows show the galaxy edge on.}
    \label{gas_column3}
\end{figure}
\begin{figure}
    \includegraphics[width=0.7\textwidth]{figures3/SMHMR.eps}
    \caption[MUGS2 stellar mass to halo mass relation]{Stellar mass versus halo
    mass at $z=0$.  The observed stellar mass to halo mass relation is from
    \citet{Hudson2015}'s weak lensing study of galaxies to $z=0.8$.  Galaxies
    that fall within this range are shown as blue squares, while galaxies above
    the curve (those which form too many stars) are shown as red circles.  For
    comparison, the black stars show galaxies from the NIHAO sample
    \citep{Wang2015}.}
    \label{SMHMR3}
\end{figure}
\begin{figure}
    \includegraphics[width=0.7\textwidth]{figures3/rotcurve.eps}
    \caption[MUGS2 rotation curves]{As is clear from the above rotation curves,
    galaxies which overproduce stars (shown in dotted red) also have large
    central concentrations, giving steeply peaked rotation curves inconsistent
    with those seen in local $L*$ galaxies.  Galaxies with well-regulated star
    formation have flat rotation curves (shown in solid blue).}
    \label{rotation_curve3}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{figures3/stellar_central.eps}
    \caption[Stellar mass vs. central baryonic mass in MUGS2 galaxies]{The stellar mass and the central baryonic mass show a tight
        correlation.  For the well-regulated population, roughly $40\%$ of the
        central baryons are stars, while for the unregulated population has
        converted $\sim70\%$ of the central baryon mass into stars.}
    \label{stellar_central3}
\end{figure}
\begin{figure}
    \includegraphics[width=0.63\textwidth]{figures3/phase.eps}
    \caption[Gas phase diagram in two MUGS2 galaxies]{Gas phase diagrams for a
    well-regulated galaxy (g24334) and an unregulated galaxy (g19195).  Colour
    shows the amount of mass at a given $\rho-T$ point.  The top phase diagram
    shows the characteristic slope for adiabatic (dashed line) and isobaric
    (dotted line) processes.  As can be seen, both galaxies are qualitatively
    the same.  Both show the equilibrium cooling curve below $10^4\K$, and both
    show the adiabatic evolution of superbubble-heated gas as it leaves the
    disc.}
    \label{phase3}
\end{figure}

The general properties of each galaxy at $z=0$ can be found in
Table~\ref{z0_table3}.  $\lambda'$ is the dimensionless spin parameter of the
halo, defined by \citet{Bullock2001} as $\lambda'=J/\sqrt{2GM_{\rm vir}^3R_{\rm vir}}$.
$f_b$ is the baryon fraction of the halo.  $z_{1/2}$ and $z_{\rm lmm}$ are the
redshifts at which the halo reaches half of its final mass, and the redshift of
last major merger respectively.  Major mergers are defined to match
\citet{Stinson2010}, as a merger with a halo containing at least $1/3$ the
stellar mass of the main progenitor.  $M_{\rm vir}$, $M_*$, and $M_{\rm gas}$ are the
masses of the full halo, the stellar component, and the gas component
respectively within the virial radius.  $\rm{SFR_{\rm z=0}}$ is the redshift 0 
SFR, averaged over the previous $100\Myr$.  The virial radius
is defined as the radius around the halo such that the enclosed density is 200
times the critical density ($\rho=200\rho_{\rm crit}$).  While we used the same
definitions for quantities reported in \citet{Stinson2010}, every value reported
here is derived from the new MUGS2 simulations.  We also define a {\it central}
region of the halo, which contains the disc and the majority of the stars within
the halo.  The baryon mass within this region is given as $M_{\rm central}$  This
central region is simply a sphere of radius $0.1R_{\rm vir}$.

Mock stellar observations and {\sc Hi} column images of these galaxies can be
seen in Figs~\ref{stellar_image3} and~\ref{gas_column3}.  The labels on each of
these images are coloured red if they are in the `unregulated' population
discussed in the next section.  The varied merger history of these galaxies is
evident in these images: companions can be seen in three galaxies (g21647,
g22795, g4145), tidal tails are evident in another  (g19195), and strong bars
exist in another two (g28547, g24334).

The {\sc Hi} column density shown in Fig.~\ref{gas_column3} shows, as was seen in
\citet{Keller2015}, large quantities of extraplanar {\sc Hi} gas, driven up by
outflows from the galaxy disc.  {\sc Hi} gas above the galactic plane has been seen
since \citet{Muller1963}.  \citet{Lockman1984} found similar column densities to
what is seen here to heights of $1.5\kpc$.  High-velocity clouds of relatively
dense ($\sim0.1\; \rm{cm^{-3}}$ gas have also been seen both leaving and
returning to the galaxy \citep{Wakker1997}.  Diffuse {\sc Hi} gas has been observed
out to $\sim300\kpc$ in absorption features of numerous nearby galaxies
\citep{Wakker2009,Prochaska2011}.  \citet{Werk2014} surveyed a number of
galaxies in the COS-haloes survey, and found that typical $L*$ galaxies contain
$\sim5 \times10^{10}\Msun$ of cool gas in their CGM.  The face-on {\sc Hi}
distribution for all but a handful of the unregulated (see the following
section) follow the \citet{Broeils1997} {\sc Hi} mass-size relation, with {\sc Hi} column
densities falling below $1\Msun\pc^{-2}$ at radii of $10-20\kpc$.  This is well
within the intrinsic scatter found in the recent observational study of
\citet{Wang2016}.

\subsection{Stellar Mass Runaway}
\begin{figure}
    \includegraphics[width=0.7\textwidth]{figures3/stellar_fraction_time.eps}
    \caption[Stellar mass fraction evolution in MUGS2]{Stellar mass fraction
    versus time.  As is clear, for the unregulated population the buildup of
    stellar mass above $\sim3\%$ of the halo mass happens very rapidly, often on
    time-scales of $\sim1\Gyr$.  The runaway in the unregulated population stops
    simply when the disc has been sufficiently depleted of gas that little
    remains to form new stars.}
    \label{stellar_fraction_time3}
\end{figure}
As can be seen in Fig.~\ref{SMHMR3}, roughly half of these galaxies fall within
the expected $z=0$ stellar mass to halo mass relation (SMHMR).  The grey band
shown in the figure is the $2\sigma$ confidence region in the observed SMHMR
from \citet{Hudson2015}, which used the CFHTLens weak lensing survey to produce
a fully-observational SMHMR, without the uncertainties of the using dark
matter-only simulations that are needed for abundance matching techniques (the
\citet{Hudson2015} SMHMR is consistent with past abundance matching estimates
such as \citet{Behroozi2013} and \citet{Moster2013}).  For the rest of this
paper, we will refer to the galaxies that fall within the $2\sigma$ confidence
interval for the observed SMHMR (i.e. galaxies where stellar feedback prevents
overproduction of stars) as {\it well-regulated}, and the galaxies where stellar
feedback fails to produce the correct SMHMR as {\it unregulated}.  No other
criterion is used for determining which population a galaxy falls into. In
addition to overproducing stars, these unregulated galaxies are qualitatively
redder and more bulge dominated, as can be seen in the mock stellar images of
Fig.~\ref{stellar_image3}.  There appears to be no significant difference in
the redshift of the last major merger between the two populations, strongly
suggesting that the failure of stellar feedback to regulate the galaxies is not
simply a matter of recent or violent merging.  The rotation curves in
Fig.~\ref{rotation_curve3} also show the distinct signature of massive bulges
formed by catastrophic angular momentum loss in the unregulated population.
\citet{vanDenBosch2001} showed that this can arise when gas simply traces the
dark matter distribution, without redistribution or ejection by feedback.  The
strong peaks (as high as $700\kms$ for g4720) come about from the central
concentration of baryons in the galaxy bulge.  Without exception, each of the
well-regulated galaxies shows a flat rotation curve, with no evidence of a
significant bulge component.  This matches the qualitative morphology seen in
Fig.~\ref{stellar_image3}.

Fig.~\ref{stellar_central3} shows that for the well-regulated population, the
stellar mass and central baryonic mass follow an extremely tight linear
relation, with a mean star formation efficiency (simply defined here as the
fraction of central baryons that are in stars) of $38\pm2\%$ over a Hubble time.
For the galaxies that fail to self-regulate, they exhibit a total star formation
efficiency of $70\pm10\%$, converting the majority of the baryons that collapse
on to their disc into stars.  Interestingly, the two populations can be divided
cleanly along the $M_{\rm central}=10^{11}\;\Msun$ or the
$M_*=5\times10^{10}\;\Msun$ axis.  This is clear evidence that what explains
the dichotomy here must involve the accretion (or the failure to remove!)
baryons from the central region of the halo, where the disc resides and stars
are formed.  These relations also help to explain some of the correlations seen
observationally, such as the critical mass of $3\times10^{10}\Msun$ that 
\citet{Kauffmann2003a} found dividing star forming and quenched galaxies in the
SDSS at low redshift.

The gas phase diagram of galaxies in the two populations is remarkably similar,
as can be seen in Fig.~\ref{phase3}.  For a representative pair from each
population, of nearly equal halo mass, gas follows essentially the same
evolutionary path, characteristic of a superbubble-regulated ISM, as was shown in
\citet{Keller2015}.  Gas accretes from the halo,
building up a warm ISM at $T\sim10^4\K$.  Where that gas reaches densities of
$\sim 1\;$cm$^{-3}$, it begins to cool quickly and form stars.  Those stars begin to
explode as SN, and a hot superbubble is formed, with $T>10^7\K$.  As the bubble
grows, it's temperature falls as it both expands adiabatically and evaporates
the cold shell surrounding it.  This hot, buoyant gas leaves the disc, rising
through the CGM and cooling adiabatically as it goes.  What is remarkable here
is just how similar the phase diagrams of these two galaxies are.  The slight
differences are what we would expect from Table~\ref{z0_table3}.  g19195 has
$\sim50\%$ less gas than g24334, and more than 3 times the SFR at $z=0$.  Thus,
there is less total material, especially in the warm and cold phases, and
slightly more of the very hot ($T>5\times10^7\K$) gas (the interiors of very young
superbubbles) as a consequence of the higher SFR.  What is important to take
away from these phase diagrams is that a well-regulated and unregulated galaxy
do not have any real difference in the phase behaviour of their gas.  There is
no runaway cooling, or failure of SN to generate hot gas:  what causes the
unregulated population to runaway is purely an effect of the outflow
effectiveness, which is set by the depth of the potential well.

\subsection{Time Evolution} 
\begin{figure}
    \includegraphics[width=0.7\textwidth]{figures3/SMHMR_time.eps}
    \caption[Stellar mass vs. halo mass evolution in MUGS2]{Stellar mass versus
    halo mass, as shown in Fig.~\ref{SMHMR3}, but with trails added to show time
    evolution.  For halo masses below $\sim\rm{a\;few}\times10^{11}$, the
    evolution of the regulated and unregulated populations are
    indistinguishable.  The grey bar shows the $z=0$ SMHMR, as in
    Fig.~\ref{SMHMR3}}
    \label{SMHMR_time3}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{figures3/stellar_central_time.eps}
    \caption[Stellar mass vs. central baryonic mass evolution in MUGS2]{Stellar
    mass versus central baryon mass. The stellar mass here can be seen to vary
    much more smoothly over the evolution, without the slight `jump' seen in
    Fig.~\ref{stellar_fraction_time3}.}
    \label{stellar_central_time3}
\end{figure}

The obvious question that arises from the presence of these two (well-regulated
versus  unregulated) populations at $z=0$ is whether they are distinct through
their entire evolution, and if not, why/how do they diverge?  Previous work
suggests that a characteristic (halo or stellar) mass exists above which AGN
feedback is needed.  There is much uncertainty, however, about where this mass
exactly is, and how the transition from SN to AGN regulation actually works. We
should thus expect galaxies to begin diverging once this characteristic mass is
exceeded.  As Fig.~\ref{stellar_fraction_time3} shows, the stellar mass
fraction for the two populations appear to follow similar evolutionary tracks
for some time (until past $z=0.5$ in the case of g19195, the galaxy which
diverges the latest).  However, once a galaxy begins to overproduce stars, it
appears to do so in a runaway, doubling or even tripling its stellar mass
fraction in less than a Gyr.

The similar early star formation history of the two populations is even more
clear if we look at the SMHMR's time evolution in Fig.~\ref{SMHMR_time3}.  Here
we can see, that for galaxies with halo masses below a few $10^{11}\;\Msun$,
the stellar mass falls well within the expected SMHMR distribution, and the two
populations are indistinguishable.  The mass at which the populations begin to
diverge ( $M_*\sim10^{10}\;\Msun$ and $M_{\rm vir}\sim\operatorname{3-
5}\times10^{11}\;\Msun$) are quite close to the expected transition range
from \citet{Shankar2006} ( $M_*\sim1.2\times10^{10}\;\Msun$ and
$M_{\rm vir}\sim3\times10^{11}\;\Msun$).

The relatively smooth change in the $M_*-M_{\rm central}$ relation, shown in
Fig.~\ref{stellar_central_time3}, shows that it is in fact the central baryon
mass that is more tightly correlated with the stellar mass than the total halo
mass (in galaxies regulated by SN feedback alone). In fact, it is likely that
some of the more massive galaxies in the well-regulated sample are on their way
to failing, but simply have not yet had enough time by $z=0$ to diverge
significantly from the observed SMHMR.  Once more than $\sim10^{11}\Msun$ of
baryons have accreted to the disc of a galaxy, SN alone appear to be unable to
halt the growth of stellar mass.  At this point, star formation efficiency of
the central disc begins to increase, from $\sim40$ to $\sim70$ per cent, resulting in
the differences seen in the two populations at $z=0$.  This accretion crisis, as
it continues to smaller scales, also explains the rotation profiles of the
unregulated population.  The overcollapse that results in runaway starformation
also builds a massive bulge, producing the peaked rotation curves seen in
Fig.~\ref{rotation_curve3}.

\subsection{Galactic Outflows}
\begin{figure}
    \includegraphics[width=0.7\textwidth]{figures3/massloading_time.eps}
    \caption[Outflow mass loading evolution in MUGS2]{Outflow mass loading
    decreases as galaxies grow over time, as was previously shown by
    \citet{Keller2015}.  Here we see, when examining the mean mass loadings for
    the two populations (the well-regulated galaxies, where stellar feedback
    succeeds, and the unregulated galaxies, where it fails), that the
    unregulated galaxies have their mass loadings decrease sooner, and to lower
    values, than the well-regulated population.  The error bars here are the
    $1\sigma$ scatter in each population.}
    \label{massloading_time3}
\end{figure}
\begin{figure}
    \includegraphics[width=0.7\textwidth]{figures3/massloading_halo.eps}
    \caption[Mass loading as a function of halo mass in MUGS2]{Unlike in the
    previous figure, if we look at mass loading as a function of halo mass, we
    instead see no significant difference between the two populations.  Instead,
    both follow a similar trajectory, and the haloes which fail to self-regulate
    do so simply because they reach a higher mass earlier.}
    \label{massloading_halo3}
\end{figure}

@@

Fig.~\ref{SMHMR3} shows that while the unregulated galaxies tend to be more
massive than the well-regulated ones, there is some overlap in the $M_{\rm
halo}=\operatorname{8-12}\times10^{12}\;\Msun$ range, where there are both
unregulated and well-regulated galaxies.  Figs~\ref{stellar_fraction_time3}
and~\ref{SMHMR_time3} show that the process of runaway star formation happens
rapidly, and can begins over a wide range of halo masses.  This is further
evidence that something beyond simply the mass of the halo that hosts a galaxy
is at play in determining whether or not SN fail to regulate the growth of that
galaxy.
